### 2024-11-22 NN/plots_latex.tex
commit

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Sig1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{Sig1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

### 2024-11-22 NN/plots_preds_latex.tex
commit

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-98.65-TanhReluFFNN-conc.png}
    \caption{Prediction of conc with TanhReluFFNN epochs:50 - R-Squared: 0.99}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-69.68-Sig1HiddenLayer-Temp.png}
    \caption{Prediction of Temp with Sig1HiddenLayer epochs:200 - R-Squared: 0.70}
\end{figure}

### 2024-11-22 NN/tables/backward.tex
commit

\begin{longtable}{lr}
\hline
 features                        &    R2 \\
\hline
 time, flowrate, temp, init conc & 98.54 \\
 flowrate, temp, init conc       &  0.66 \\
 time, temp, init conc           & 94.34 \\
 time, flowrate, init conc       & 98.02 \\
 time, flowrate, temp            & 95.41 \\
\hline
\end{longtable}

>>>>

\begin{longtable}{lr}
\hline
 features                                                                                                                                    &    R2 \\
\hline
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m & 82.44 \\
 Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m             & 76.24 \\
 SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m               & 76.24 \\
 SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m            & 76.24 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m                     & 78.37 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m         & 75.31 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m                 & 77.73 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp, m                   & 76.41 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp, m            & 74.24 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp, m                  & 75.63 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), m            & 65.18 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp    & 61.71 \\
\hline
\end{longtable}

### 2024-11-22 NN/tables/forward.tex
commit

\begin{longtable}{lr}
\hline
 features                        &    R2 \\
\hline
 time                            & 93.84 \\
 flowrate                        & -0.79 \\
 temp                            &  0.69 \\
 init conc                       &  1.47 \\
 flowrate, time                  & 95.32 \\
 temp, time                      & 93.29 \\
 init conc, time                 & 94.95 \\
 temp, time, flowrate            & 95.21 \\
 init conc, time, flowrate       & 97.84 \\
 temp, time, flowrate, init conc & 97.39 \\
\hline
\end{longtable}

>>>>

\begin{longtable}{lr}
\hline
 features         &     R2 \\
\hline
 Pco2             &  -4.32 \\
 Pch4             & -14.19 \\
 rate             &  57.65 \\
 Pco2, rate       &  60.73 \\
 Pch4, rate       &  53.38 \\
 Pch4, rate, Pco2 &  41.27 \\
\hline
\end{longtable}
